Estimating associations between childhood exposure to non-persistent endocrine disruptors, corticosteroids, and neurodevelopment: A study based on the parametric g-formula

### 2023-12-21 output/paper/_tables.qmd
Writing results.

tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

>>>>

tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = NULL,
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$table
```

### 2023-12-21 output/paper/manuscript.qmd
Writing results.

@@

@Fig-marginal-1 presents the forest plot for the marginal effects of the non-persistent \acr{edcs} on \acr{hitrtse}. Overall, a cohort-specific increase in the levels of the exposures from the 10th to the 90th percentiles was associated with a positive marginal contrast, indicating an increase in the values of \acr{hitrtse}. Most of the \acr{ci} included the null effect, though. Statistically significant associations were observed for the phenol MEPA (\acr{mc} = $0.042$, $95\%$ \acr{ci}: $0.013, 0.071$), and the phthalate metabolites oxo-MiNP (\acr{mc} = $0.023$, $95\%$ \acr{ci}: $0.003, 0.044$), oh-MiNP (\acr{mc} = $0.039$, $95\%$ \acr{ci}: $0.001, 0.076$), and MEHP (\acr{mc} = $0.036$, $95\%$ \acr{ci}: $0.008, 0.063$). The \acr{opp} DETP was strongly negatively associated with \acr{hitrtse} (\acr{mc} = $-0.026$, $95\%$ \acr{ci}: $-0.054, 0.001$).

@Fig-marginal-2 presents the forest plot for the marginal effects of the non-persistent \acr{edcs} on cortisol production, cortisone production, corticosterone production, and 11bHSD activity, respectively.

@@

<!-- {{< include _tables.qmd >}} -->

@@

<!-- {{< include _si.qmd >}} -->

>>>>

```{r}
format_res <- function(df, exposure, outcome) {
  # df: variable, val, estimate, outcome, class
  # exposure in variable, outcome in outcome

  val <- df[df$variable == exposure & df$outcome == outcome, ]$val
  val <- stringr::str_replace(
    string = val,
    pattern = "\\*",
    replacement = ""
  )
  glue::glue(
    "\\acr{{mc}} and $95\\%$ \\acr{{ci}}: {val}"
  )
}
```

```{r}
#| echo: false

targets::tar_load(
  dplyr::matches("marginal_comparisons_(\\d)$"),
  store = store
)
meffects1 <- tidy_res_meffects(
  df = marginal_comparisons_1,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$numerical_results
meffects2 <- tidy_res_meffects(
  df = marginal_comparisons_2,
  sa_var = NULL,
  outcome = c(
    "cortisol production",
    "cortisone production",
    "corticosterone production"
  ),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$numerical_results
meffects3 <- tidy_res_meffects(
  df = marginal_comparisons_3,
  sa_var = NULL,
  outcome = c("hitrtse"),
  which_res = "comparisons",
  num_digits_est = num_digits_est,
  num_digits_sig = num_digits_sig
)$numerical_results
```

@@

@Fig-marginal-1 presents the forest plot for the marginal effects of the non-persistent \acr{edcs} on \acr{hitrtse}. Overall, a cohort-specific increase in the levels of the exposures from the 10th to the 90th percentiles was associated with a positive marginal contrast, indicating an increase in the values of \acr{hitrtse}. Most of the \acr{ci}s included the null effect, though. Statistically significant associations were observed for the phenol MEPA (`r format_res(meffects1, "mepa", "hitrtse")`), and the phthalate metabolites oxo-MiNP (`r format_res(meffects1, "oxominp", "hitrtse")`), oh-MiNP (`r format_res(meffects1, "ohminp", "hitrtse")`), and MEHP (`r format_res(meffects1, "mehp", "hitrtse")`). The \acr{opp} DETP was strongly negatively associated with \acr{hitrtse} (`r format_res(meffects1, "detp", "hitrtse")`).

@Fig-marginal-2 presents the forest plot for the marginal effects of the non-persistent \acr{edcs} on cortisone production, cortisol production, and corticosterone production. Overall, a cohort-specific increase in the levels of the exposures from the 10th to the 90th percentiles was associated with a positive marginal contrast, indicating an increase in the total production of these metabolites, with the exception of BUPA, which was associated with negative marginal contrasts for all three outcomes, and MiBP, which was associated with a negative marginal contrast for total cortisone production only.
The majority of the associations for the phenols and phthalate metabolites included the null. The phenol BPA showed the largest marginal contrasts across all three outcomes (cortisone production, `r format_res(meffects2, "bpa", "cortisone production")`; cortisol production, `r format_res(meffects1, "bpa", "cortisol production")`; corticosterone production, `r format_res(meffects1, "bpa", "corticosterone production")`).

@@

{{< include _tables.qmd >}}

@@

{{< include _si.qmd >}}
